Robust receding horizon control for linear systems with state and input dependent disturbances

### 2015-04-21 draft_v2.tex
section 6 and abstract

\title{Robust receding horizon control for linear systems with state dependent disturbance}

@@

\begin{abstract}                % Abstract of not more than 250 words.

\end{abstract}

\begin{keyword}
-
\end{keyword}

@@

\section{Problem Statement}\label{sec:problem:statement}
We consider a computationally efficient method for solving online min-max receding horizon control problems
that exploits the structure of multi-parametric programming solutions. Our approach determines the optimal
feedback law without approximating the cost or the constraints of the problem, and without making restrictive
assumptions on the parametrisation of control inputs.
%This broadens the applicability of the approach, allowing for higher order models and longer
%prediction horizons than 
%
%The high computational complexity of online min-max receding horizon control schemes generally requires either
%that the solution is approximated or that their application is limited to problems involving simple system models and short horizons. Here we consider an
%efficient method for solving min-max problems that exploits the structure of multi-parametric programming
%solutions.
%The set of systems to which a min-max robust receding horizon control scheme can be applied online 
%without approximating the solution is bounded by the system complexity. The way to solve min-max problems we 
%adopt here, is to use the structure of the solution to derive multi-parametric programs that can be solved
%efficiently. In order to be able to obtain a closed form solution of the min-max program simple optimisation
%formulations have to be
%The algorithmic treatment of min-max problems
%involving state constraints and disturbances constrained to lie in fixed polytopic disturbance sets was
%introduced in~\cite{Bertsekas:1971}. Recently~\cite{Schaich:2015} proposed an algorithm to compute the so called maximal
%robust positive invariant (MRPI) sets (see~\cite{blanchini:2007}) for linear systems subject to state and
%input dependent disturbance constraints. In this paper we develop the algorithm further
%to compute polytopic constraints necessary to satisfy state constraints robustly in this setup. We
%present a robust receding horizon control scheme for
%
To make it possible to obtain a closed form solution of the min-max optimal control problem we assume a
linear-quadratic problem formulation. Thus we assume the linear dynamic model 
\begin{equation}\label{eq:system:equation}
	x^+ = A x + B u + D w,
\end{equation}
%
where $A,B,D$ are real matrices of appropriate dimension, $x,  x^+\in\mathcal X\subseteq\mathbb R^n$ denote the state 
and successor state respectively, $u\in\mathcal U=\{u:Fu\leq{\bf{1}}\}\subset\mathbb R^p$ is the control input
and $w\in\mathcal W(x,u)\subset\mathbb R^q$ is an unknown disturbance input. The disturbance set $\mathcal
W(x,u)$ is assumed to have a known dependence on the values of $x$ and $u$, according to
%
\begin{equation}\label{eq:PWA:def:disturbance}
	\mathcal W(x,u) = \{w: Gw \leq H(x,u)\},
\end{equation}
%
where $H(x,u)$ is an elementwise convex, piecewise affine function. The control objective is to minimize the
worst case value, over all future model uncertainty, of the cost
\begin{equation}\label{eq:quadratic:cost}
\sum_{k=0}^\infty \bigl( \|x_k\|_Q^2 + \|u_k\|_R^2 - \gamma^2 \|w_k\|^2 \bigr) ,
\end{equation}
where the subscript $k$ denotes the realisation of a variable at time $k$, $\|x\|_Q^2$ denotes the quadratic
form $x^TQx$, $Q$ and $R$ are given positive definite
matrices and $\gamma$ is a given scalar weight that controls the $l^2$-gain of the closed loop system from the
disturbance sequence to the state and control sequences.

Given a prediction horizon of $N$ steps over which the predicted control law is to be optimized, we define the
min-max optimal control problem with $m$ stages to go as
%
\begin{subequations}\label{eq:the:problem}%
\begin{equation}
	J_{m}^\ast(x) = \min_u \max_{w,x^+} \tfrac{1}{2}\bigl(\norm{x}_Q^2+\norm{u}_R^2-\gamma^2
    \norm{w}^2\bigr) + J_{m-1}^\ast(x^+)
\end{equation}
subject to
\begin{gather}
	x^+ = A x + B u + D w\\
	u\in\mathcal U \\
	w\in\mathcal W(x,u) \\
	(x,u)\in\mathcal Z_m
\end{gather}
\end{subequations}
%
for $m=1,\ldots,N$, with $J_0^\ast(x) = \|x\|_{P_0}^2$.
The stagewise  state and input constraints $\mathcal Z_m$ are defined recursively by
%
\begin{subequations}\label{eq:definition:stage:constraints}
\begin{align}
	\mathcal Z_m &= \{(x,u)\,: u\in\mathcal U \nonumber\\
	&\quad\ \wedge \; A x + Bu + Dw\in\mathcal X_{m-1}\; \forall\, w\in\mathcal W(x,u)\} 
	\label{eq:definition:mixed:stage:constraint}\\
	\mathcal X_m &= \{x : \exists\, u\in\mathcal U, (x,u)\in\mathcal Z_m\}
	\label{eq:definition:state:stage:constraint}\\
\end{align}
with
\begin{equation}
	\mathcal X_0 = \mathcal X^\infty .
\end{equation}
\end{subequations}
Thus the constraints $(x,u)\in\mathcal Z_m$ ensure that the terminal state, namely $x^+$ at $m=1$, is
contained in $\mathcal{X}^\infty$. We define $\mathcal{X}^\infty$ as the maximal robust positive invariant (MRPI) set \citep{blanchini:2007}), for the closed-loop system governed by a fixed state feedback controller
$u=Kx$, so that 
%
\begin{equation}\label{eq:definition:MRPI:set}
	\mathcal X^\infty = \{x: (A+BK)x + Dw \in \mathcal X^\infty \forall w\in\mathcal W(x,Kx)\},
\end{equation}
%
and we define $P_0$ so that $J_0^\ast(x)$ is the worst case value of the cost (\ref{eq:quadratic:cost}) under
$u=Kx$ in the absence of constraints.
Recently~\cite{Schaich:2015} proposed an algorithm to compute MRPI sets
for linear systems subject to state and input dependent disturbance constraints. In this paper we combine this approach
with the multistage multi-parametric programming method of~\cite{Buerger:ACC} to derive an efficient algorithmic
solution to the online MPC optimization of (\ref{eq:the:problem}a-e).

@@

be non-negative, i.e.~$\eta^\ast\geq0$. Notice that we omit stage indices to avoid overloaded notation.

@@

i.e.\ $C_1^x$ and $C_1^u$ are given as a row wise normalised version of~\eqref{prototype:compatibility:conditions}.

@@

	\min_{u} & \frac{1}{2}\left(\norm{x}^2_Q + \norm{u}_R^2\right) + \hat J_{1}^\ast(x,u)\\
    \text{s.t.} & 

@@

	\end{array}\right) = \left(\begin{array}{c}K^u_x\\ O^{\nu}_x \\ O^{\hat\zeta}_x

@@

	\left(\begin{array}{c}0\\ O^{\nu}_\beta \\ O^{\hat\zeta}_{\beta}
	\end{array}\right)\beta + \left(\begin{array}{c}k^u\\ o^{\nu} \\ o^{\hat\zeta}

@@

Here $\hat C_2$ is a normalised version of $O^T_\beta(\bar T x + \bar e) = 0$.
For completeness, the $m=2$ maximisation and its solution are:

@@

	\max_{w,x^+} & -\frac{\gamma^2}{2}\norm{w}^2 + J_{1}^\ast(x^+)\\
	\text{s.t.} & 

@@

@@

\section{Exact solution of min-max program}\label{sec:line:search}
In the previous section we presented a recursive algorithm to solve~\eqref{eq:the:problem}
when all active constraints are known. In this section we present a method to find the active
constraints for a given initial state $\mathpzc x_e$ using a line search starting from a state $\mathpzc x_0$
for which the active constraints are known. In Section~\ref{sec:gen:mpQP} and~\ref{sec:applied:mpQP}
we derived an explicit solution for each sub-optimisation program which depended affinely on the
state~$x$ at that stage~$m$ or the state and the input at that stage. Henceforth we denote the stage 
with an index, e.g.~$x_m$ denotes the optimised state in stage $m$, that is $x^{+,\ast}$ at stage $m+1$.
To ensure continuity of the dual variables we choose $\hat\zeta_m = \hat\beta_m$ and $\zeta_m=\beta_{m-1}$.
The affine character of the solution of each sub-problem allows us to parametrise the entire trajectory
with respect to parameters at stage~$m=N$, that is $x_N=\chi_0$ $x_N=\mathpzc x_0$ and $\beta_N$.

We recursively define all primal and dual variables:
\begin{equation}\label{eq:trajectory:affine:representation}
	\begin{split}
		u_N(x_N) =& \underbrace{K_{x,N}^x}_{\Psi_N^u} x_N + \underbrace{k_N^u}_{\psi_N^u}\\
		\nu_N(x_N,\beta_N) &= \underbrace{O_{x,N}^x}_{\Psi_N^\nu} x_N + \underbrace{O_{\beta,N}^\nu}_{\Phi_N^\nu} \beta_N + 
		\underbrace{o_N^\nu}_{\psi_N^u}\\
		&\vdots \\
		x_0(x_N) =& \underbrace{M_{z,1}^{x^+}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right)}_{\Psi_1^x}x_N + 
		M_{z,1}^{x^+}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + m_1^{x^+}\\
		\eta_1(x_N,\beta_N) =& \underbrace{\left(N_{z,1}^{\eta}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right) + 
		N_{\hat\beta,1}^\eta \Psi_1^{\hat\zeta}\right)}_{\Psi_1^\eta}x_N + \underbrace{N_{\hat\beta,1}^\eta \Phi_1^{\hat\zeta}}_{\Phi_1^\eta} \beta_N\\
		&+\underbrace{N_{z,1}^{\eta}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + 
		N_{\hat\beta,1}^\eta \psi_1^{\hat\zeta} + n_1^\eta}_{\psi_1^\eta}\\
		&\vdots
	\end{split}
\end{equation}
Notice that $\Phi^{(\cdot)}_m$ is only non-trivial if the associated sub-problem is degenerate. The 
representation~\eqref{eq:trajectory:affine:representation} is valid as long as the constraint set remains unchanged, 
i.e. the inequalities that hold with equality do not change. Starting from the known set of active constraints at
$\mathpzc x_0$ we perform a line search towards $\mathpzc x_e$, i.e. we vary $x_N(\alpha)=\mathpzc x_0+
\alpha(\mathpzc x_e-x_0)$ for $0\leq\alpha\leq1$. We use~\eqref{eq:trajectory:affine:representation} to
check all inactive constraints with the primal variables $x_m(x_N(\alpha)),\, u_m(x_N(\alpha))$ and~$w_m(x_N(\alpha))$,
and all dual variables corresponding to inequality constraints to check whether constraints need to be deactivated. That is,
we search for the smallest $\alpha$ such that $\Xi_{m,i}^x x_m(x_N(\alpha))+\Xi_{m,i}^u u_m(x_N(\alpha))=\xi_{m,i}$
et cetera for the primal variables and the smallest $\eta_{m,i}(x_N(\alpha),\beta_N)=0$ and update the set of active
constraints accordingly, i.e. if an additional constraint is activated it is introduced to the equality constraint
mpQP recursion and the updated problems are solved again recursively, if a constraint needs to be deactivated
because the smallest $\alpha$ corresponds to the zero-crossing of its dual variable then again the mpQP recursion 
is solved again. The updated active set is the new known active set at $\mathpzc x_0 = x_N(\alpha)$ and the line-search
continues until the state~$\mathpzc x_e$ is in the same active set as $\mathpzc x_N(\alpha)$ where the line-search terminates.
To initialise we start at the origin $\mathpzc x_0=0$, since we know that no constraints are active.

Notice that in since the right hand side of~\eqref{eq:PWA:def:disturbance} is considered to be piecewise affine, the active 
affine function needs to be determined in a similar fashion. Elementwise $H(x_k(\alpha),u_k(\alpha))$ reduces to 
\begin{equation}
\Resize{
\begin{split}
	H_i(x_k(\alpha),u_k(\alpha)) &= \max_j\{\left(H^x_{i,j} \Psi^x_k +H^u_{i,j}\Psi^u_k\right)x_N(\alpha) + 
	\left(H^x_{i,j} \psi^x_k +H^u_{i,j}\psi^u_k + h_{i,j}\right) \}\\
	&=\max_j f_j\alpha + g_j
	\end{split}
}
\end{equation}
which we can rewrite as
\begin{equation}\label{eq:definition:as:mpLP}
	H_i(x_k(\alpha),u_k(\alpha)) = \left\{\begin{array}{rcl} \min_{(t,\alpha)}& &t\\
	\text{s.t.}& &f_j\alpha+g_j \leq t\; \forall j.\\
	& &0\leq\alpha\leq1
	\end{array}\right.
\end{equation}
So elementwise the determination of the active affine representation is a multi-parametric linear program, see e.g.~\cite{Gal:1995},
that has to be solved in every active set update. So that $W_x^\prime,\,W_u^\prime$ and $w^\prime_c$ remain the active
solution. This can be done by computing the vertices of $\mathcal H = \{(t,\alpha):0\leq\alpha\leq1\wedge
f_j\alpha+g_j\leq t\;\forall j\}$ and ordering the vertices such that $0=\alpha_1\leq\alpha_2\leq\dots$ the solution
that has to be considered in the line search is given by $\alpha_2$.

>>>>

\title{Robust receding horizon control for linear systems with state and input dependent disturbances}

@@

\begin{abstract}                % Abstract of not more than 250 words.
  A robust model predictive controller is proposed for constrained linear systems with unknown disturbances
  that are subject to state and input dependent piecewise affine bounds.
  % with a dependence on the system state and control input. 
  The formulation encompasses problems involving model uncertainty arising from unknown system
  parameters and linearisation errors. We propose a computationally efficient method for the online
  optimization of a receding horizon min-max cost over the class of feedback strategies subject robust
  constraint satisfaction and provide illustrative numerical examples.
\end{abstract}

\begin{keyword}
Robust optimal control, min-max control, multiparametric programming 
\end{keyword}

@@

\section{Problem Statement}\label{sec:problem:statement}
We consider a computationally efficient method for solving online min-max receding horizon control problems
that exploits the structure of multi-parametric programming solutions. Our approach determines the optimal
feedback law without approximating the cost or the constraints of the problem, and without making restrictive
assumptions on the parametrisation of control inputs.
%This broadens the applicability of the approach, allowing for higher order models and longer
%prediction horizons than 
%
%The high computational complexity of online min-max receding horizon control schemes generally requires either
%that the solution is approximated or that their application is limited to problems involving simple system models and short horizons. Here we consider an
%efficient method for solving min-max problems that exploits the structure of multi-parametric programming
%solutions.
%The set of systems to which a min-max robust receding horizon control scheme can be applied online 
%without approximating the solution is bounded by the system complexity. The way to solve min-max problems we 
%adopt here, is to use the structure of the solution to derive multi-parametric programs that can be solved
%efficiently. In order to be able to obtain a closed form solution of the min-max program simple optimisation
%formulations have to be
%The algorithmic treatment of min-max problems
%involving state constraints and disturbances constrained to lie in fixed polytopic disturbance sets was
%introduced in~\cite{Bertsekas:1971}. Recently~\cite{Schaich:2015} proposed an algorithm to compute the so called maximal
%robust positive invariant (MRPI) sets (see~\cite{blanchini:2007}) for linear systems subject to state and
%input dependent disturbance constraints. In this paper we develop the algorithm further
%to compute polytopic constraints necessary to satisfy state constraints robustly in this setup. We
%present a robust receding horizon control scheme for
%
To make it possible to obtain a closed form solution of the min-max optimal control problem we assume a
linear-quadratic problem formulation. Thus we assume linear dynamics 
\begin{equation}\label{eq:system:equation}
	x^+ = A x + B u + D w,
\end{equation}
%
where $A,B,D$ are real matrices of appropriate dimension, $x,  x^+\in\mathcal X\subseteq\mathbb R^n$ denote the state 
and successor state respectively, $u\in\mathcal U=\{u:Fu\leq{\bf{1}}\}\subset\mathbb R^p$ is the control input
and $w\in\mathcal W(x,u)\subset\mathbb R^q$ is an unknown disturbance input. The disturbance set $\mathcal
W(x,u)$ is assumed to have a known dependence on the values of $x$ and $u$, according to
%
\begin{equation}\label{eq:PWA:def:disturbance}
	\mathcal W(x,u) = \{w: Gw \leq H(x,u)\},
\end{equation}
%
where $H(x,u)$ is an elementwise convex, piecewise affine function. The control objective is to minimize the
worst case value, over all future model uncertainty, of the cost
\begin{equation}\label{eq:quadratic:cost}
\sum_{k=0}^\infty \bigl( \|x_k\|_Q^2 + \|u_k\|_R^2 - \gamma^2 \|w_k\|^2 \bigr) ,
\end{equation}
where the subscript $k$ denotes the realisation of a variable at time $k$, $\|x\|_Q^2$ denotes the quadratic
form $x^TQx$, $Q$ and $R$ are given positive definite
matrices and $\gamma$ is a given scalar weight that controls the $l^2$-gain of the closed loop system from the
disturbance sequence to the state and control sequences.

Given a prediction horizon of $N$ steps over which the predicted control law is to be optimized, we define the
min-max optimal control problem with $m$ stages to go as
%
\begin{subequations}\label{eq:the:problem}%
\begin{equation}
	J_{m}^\ast(x) = \min_u \max_{w,x^+} \tfrac{1}{2}\bigl(\norm{x}_Q^2+\norm{u}_R^2-\gamma^2
    \norm{w}^2\bigr) + J_{m-1}^\ast(x^+)
\end{equation}
subject to
\begin{gather}
	x^+ = A x + B u + D w\\
	u\in\mathcal U \\
	w\in\mathcal W(x,u) \\
	(x,u)\in\mathcal Z_m
\end{gather}
\end{subequations}
%
for $m=1,\ldots,N$, with $J_0^\ast(x) = \|x\|_{P_0}^2$.
The stagewise  state and input constraints $\mathcal Z_m$ are defined recursively by
%
\begin{subequations}\label{eq:definition:stage:constraints}
\begin{align}
	\mathcal Z_m &= \{(x,u)\,: u\in\mathcal U \nonumber\\
	&\quad\ \wedge \; A x + Bu + Dw\in\mathcal X_{m-1}\; \forall\, w\in\mathcal W(x,u)\} 
	\label{eq:definition:mixed:stage:constraint}\\
	\mathcal X_m &= \{x : \exists\, u\in\mathcal U, (x,u)\in\mathcal Z_m\}
	\label{eq:definition:state:stage:constraint}\\
\end{align}
with
\begin{equation}
	\mathcal X_0 = \mathcal X^\infty .
\end{equation}
\end{subequations}
Thus the constraints $(x,u)\in\mathcal Z_m$ ensure that the terminal state, namely $x^+$ at $m=1$, is
contained in $\mathcal{X}^\infty$. We define $\mathcal{X}^\infty$ as the maximal robust positive invariant (MRPI) set \citep{blanchini:2007}), for the closed-loop system governed by a fixed state feedback controller
$u=Kx$:
%
\begin{equation}\label{eq:definition:MRPI:set}
	\mathcal X^\infty = \{x: (A+BK)x + Dw \in \mathcal X^\infty \forall w\in\mathcal W(x,Kx)\},
\end{equation}
%
and we define $P_0$ so that $J_0^\ast(x)$ is the worst case value of the cost (\ref{eq:quadratic:cost}) under
$u=Kx$ in the absence of constraints.
Recently~\cite{Schaich:2015} proposed an algorithm to compute MRPI sets
for linear systems subject to state and input dependent disturbance constraints. In this paper we combine this approach
with the multistage multi-parametric programming method of~\cite{Buerger:ACC} to derive an efficient algorithmic
solution to the online MPC optimization of (\ref{eq:the:problem}a-e).

@@

be non-negative, i.e.~$\eta^\ast\geq0$. Notice that to avoid
overloaded notation we have omitted the stage indices.

@@

i.e.\ $C_1^x$ and $C_1^u$ enforce a row wise normalised version of~\eqref{prototype:compatibility:conditions}.

@@

	\min_{u} \ & \frac{1}{2}\left(\norm{x}^2_Q + \norm{u}_R^2\right) + \hat J_{1}^\ast(x,u)\\
    \text{s.t.} \ & 

@@

	\end{array}\right) = \left(\begin{array}{c}K^u_x\\ L^{\nu}_x \\ L^{\hat\zeta}_x

@@

	\left(\begin{array}{c}0\\ L^{\nu}_\beta \\ L^{\hat\zeta}_{\beta}
	\end{array}\right)\beta + \left(\begin{array}{c}k^u\\ l^{\nu} \\ l^{\hat\zeta}

@@

For completeness the $m=2$ maximisation and its solution are given as
\begin{gather*}

@@

	\max_{w,x^+} \ & {-\frac{\gamma^2}{2}}\norm{w}^2 + J_{1}^\ast(x^+)\\

@@

\end{gather*}
where $\hat C_2 x = {\bf{1}}$ is a normalised version of $L^T_\beta(\bar T x + \bar e) = 0$.

@@

\section{Exact solution of min-max program}\label{sec:line:search}
The previous section presents a recursive algorithm to solve~\eqref{eq:the:problem}
when all active constraints are known. In this section we present a method to find the active
constraints for a given initial state $\chi_e$ using a line search starting from a state $\chi_0$
for which the active constraints are known. In Sections~\ref{sec:gen:mpQP} and~\ref{sec:applied:mpQP}
we derived an explicit solution for each optimisation sub-problem which depends affinely on the
state~$x$ at that stage~$m$ or the state and the input at that stage. Henceforth we denote the stage 
with an index, e.g.~$x_m$ denotes the optimised state in stage $m$, that is $x^{+,\ast}$ at stage $m+1$.
To ensure continuity of the dual variables we choose $\hat\zeta_m = \hat\beta_m$ and $\zeta_m=\beta_{m-1}$.
The affine character of the solution of each sub-problem allows us to parametrise the entire trajectory
with respect to parameters at stage~$m=N$, that is $x_N=\chi_0$ and $\beta_N$.

We recursively define all primal and dual variables:
\begin{equation}\label{eq:trajectory:affine:representation}
	\begin{split}
		u_N(x_N) =& \underbrace{K_{x,N}^x}_{\Psi_N^u} x_N + \underbrace{k_N^u}_{\psi_N^u}\\
		\nu_N(x_N,\beta_N) &= \underbrace{L_{x,N}^x}_{\Psi_N^\nu} x_N + \underbrace{L_{\beta,N}^\nu}_{\Phi_N^\nu} \beta_N + 
		\underbrace{l_N^\nu}_{\psi_N^u}\\
		&\vdots \\
		x_0(x_N) =& \underbrace{M_{z,1}^{x^+}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right)}_{\Psi_1^x}x_N + 
		\underbrace{M_{z,1}^{x^+}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + m_1^{x^+}}_{\psi^x_1}\\
		\eta_1(x_N,\beta_N) =& \underbrace{\left(N_{z,1}^{\eta}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right) + 
		N_{\hat\beta,1}^\eta \Psi_1^{\hat\zeta}\right)}_{\Psi_1^\eta}x_N + \underbrace{N_{\hat\beta,1}^\eta \Phi_1^{\hat\zeta}}_{\Phi_1^\eta} \beta_N\\
		&+\underbrace{N_{z,1}^{\eta}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + 
		N_{\hat\beta,1}^\eta \psi_1^{\hat\zeta} + n_1^\eta}_{\psi_1^\eta}\\
		&\vdots
	\end{split}
\end{equation}
Notice that $\Phi^{(\cdot)}_m$ is only non-trivial if the associated sub-problem is degenerate. The
representation~\eqref{eq:trajectory:affine:representation} is valid as long as the constraint set remains
unchanged, i.e.\ the inequalities that hold with equality do not change. Starting from the known set of active
constraints at $\chi_0$ we perform a line search towards $\chi_e$, i.e. we vary
$x_N(\alpha)=\chi_0+ \alpha(\chi_e-x_0)$ for $0\leq\alpha\leq1$. We
use~\eqref{eq:trajectory:affine:representation} to check all inactive constraints with the primal variables
$x_m(x_N(\alpha)),\, u_m(x_N(\alpha))$ and~$w_m(x_N(\alpha))$, and all dual variables corresponding to
inequality constraints to check whether constraints need to be deactivated. That is, we search for the
smallest $\alpha$ such that $\Xi_{m,i}^x x_m(x_N(\alpha))+\Xi_{m,i}^u u_m(x_N(\alpha))=\xi_{m,i}$ or
$G_iw_m(x_N(\alpha))=1$ or $\eta_{m,i}(x_N(\alpha),\beta_N)=0$ for some $m$ and $i$, and update the set of active
constraints accordingly, i.e. if an additional constraint is activated it is introduced to the equality
constraint mpQP recursion and the updated problems are solved again recursively, if a constraint is
deactivated because the smallest $\alpha$ corresponds to the zero-crossing of its dual variable then it is
removed and the
mpQP recursion is solved again. The updated active set is the new known active set at $\chi_0 = x_N(\alpha)$
and the line-search continues until the state~$\chi_e$ is in the same active set as $\chi_N(\alpha)$ where the
line-search terminates.  To initialise we start at the origin $\chi_0=0$, since we know that no constraints
are active.

Notice that since the right hand side of~\eqref{eq:PWA:def:disturbance} is considered to be piecewise affine, the active 
affine function needs to be determined in a similar fashion. Elementwise $H(x_k(\alpha),u_k(\alpha))$ reduces to 
\[
\begin{split}
	H_i(x_k(\alpha),u_k(\alpha)) &= \begin{aligned}[t] \max_j\{ & \left(H^x_{i,j} \Psi^x_k
          +H^u_{i,j}\Psi^u_k\right)x_N(\alpha)\\
        & + \left(H^x_{i,j} \psi^x_k +H^u_{i,j}\psi^u_k + h_{i,j}\right) \}
        \end{aligned}\\
	&=\max_j f_j\alpha + g_j
	\end{split}
\]
which we can rewrite as
\begin{equation}\label{eq:definition:as:mpLP}
	H_i(x_k(\alpha),u_k(\alpha)) = \left\{\begin{array}{rcl} \min_{(t,\alpha)}& &t\\
	\text{s.t.}& &f_j\alpha+g_j \leq t\; \forall j.\\
	& &0\leq\alpha\leq1
	\end{array}\right.
\end{equation}
Thus the elementwise determination of the active affine representation is a multi-parametric linear program
\citep[see e.g.][]{Gal:1995} that has to be solved in every active set update in order that $W_x^\prime,\,W_u^\prime$
and $w^\prime_c$ provide the active solution. This can be done by computing the vertices of
$\mathcal H = \{(t,\alpha):0\leq\alpha\leq1\wedge f_j\alpha+g_j\leq t\;\forall j\}$ and ordering the vertices
such that $0=\alpha_1\leq\alpha_2\leq\dots$ the solution that has to be considered in the line search is then given
by $\alpha_2$.
